NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-06-22 paper/application.tex
update response

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the
To illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model,
\shusen{we present five interconnected application scenarios a domain expert may employ in their analysis workflow.
For example, the users can start the exploration by examining the stability of prediction (Scenario 1), from which they may identify the individual instances worth further investigation (Scenario 2, 3, 4). Alternatively, the user can also start with handcrafted common/extreme cases (Scenario 5) and further the exploration based on the instantaneous feedbacks provide by the visualization tool.
}
%we present five application scenarios
%(first three roughly correspond to \textbf{T1-3}) gathered by the domain experts who integrated the proposed tool into their analysis workflow.

@@

Interestingly, all configurations except one are concentrated around the full \emph{neutral} prediction. Referring back to the pipeline visualization, we observe that the only configuration that failed to produce the correct label is the one for which we allow only updating of the attention stage of the model.
%
%In other words, the updating of the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder stage of the model.
%Similar observations can be obtained for most examples we have experimented with.
\shusen{
The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
The domain experts suggest a preliminary understanding as the following.
Attention provides a way to compose word semantics. Individual word semantics are yielded by the encoder and input embedding, while the composed semantics participate in classification layer. We can see from this analysis that, only adjusting the word alignment only affects composed semantics but has no effect on word semantics while the later plays a significant role in good model (as this was also justified by recent works in word embeddings, e.g. Elmo). Without proper semantics (in both encoder and classifier), only adjusting alignment is not sufficient to yield good model. 
%To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
%In our case, the result indicates that the tunable parameters of the attention stage (the transformation before the alignment operation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
%However, this result does not necessarily imply the limitation of attention mechanism as the core alignment computation does not have tunable parameters that can be modified by the proposed optimization.
}
%The attention layer is less sensitive compared to encoding layer and classification layer.
%When examined other sentences pairs, such an observation remains.
%This gives domain expert some hint about the significance of the role of each pipeline stage play in this model.
% which based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network generalize the concept of maligin combined effort of the  proposed technique

>>>>

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the
To illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model,
we present five interconnected application scenarios a domain expert may employ in their analysis workflow.
The user can start the exploration by examining the stability of prediction (Scenario 1), from which they may identify the individual instances worth further investigation (Scenario 2, 3, 4). Alternatively, the user can begin with handcrafted common/extreme cases (Scenario 5) and continue from there.
%we present five application scenarios
%(first three roughly correspond to \textbf{T1-3}) gathered by the domain experts who integrated the proposed tool into their analysis workflow.

@@

Interestingly, all configurations except one are concentrated around the full \emph{neutral} prediction. Referring back to the pipeline visualization, we observe that the only configuration that failed to produce the correct label is the one for which we allow only updating of the attention stage of the model.
%
%In other words, the updating of the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder stage of the model.
%Similar observations can be obtained for most examples we have experimented with.
%\shusen{
%The domain experts comment that this observation is interesting and worth further investigation from the perspective of NLP research.
The domain experts find this observation very interesting and suggest a preliminary interpretation. They believe the attention provides a way to compose word semantics. Individual word semantics are yielded from the encoder and input embedding, while the composed semantics participate in classification layer. From this analysis, we can extrapolate that adjusting the word alignment affects only the composed semantics but has no effect on word semantics, which often plays a significant role in a good model (as supported by recent works in word embeddings, e.g., ELMo~\cite{salant2017contextualized}). Without proper semantics (in both encoder and classifier), only adjusting alignment is not sufficient to yield good model. 
%To interpret the result, we need to carry out a case by case analysis, as the separation of the stages depends on the individual implementation.
%In our case, the result indicates that the tunable parameters of the attention stage (the transformation before the alignment operation, see details in Appendix A) has less impact on the final prediction compared to the other two stages.
%However, this result does not necessarily imply the limitation of attention mechanism as the core alignment computation does not have tunable parameters that can be modified by the proposed optimization.
%}
%The attention layer is less sensitive compared to encoding layer and classification layer.
%When examined other sentences pairs, such an observation remains.
%This gives domain expert some hint about the significance of the role of each pipeline stage play in this model.
% which based on the natural extension of the margin-infused relaxed algorithm (MIRA) to the neural network generalize the concept of maligin combined effort of the  proposed technique

### 2018-06-22 paper/intro.tex
integrated the comment and update the paper
update response

Compared to image classification tasks, natural language processing (NLP) systems often involve additional challenges such as the discrete nature of words.
For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) captures, cannot be readily generalized to natural language.
\shusen{
An image (pixel values) corresponds to a continuous solution space. which is more accessable for optimization and human visual recognation (i.e., the existence or the absence of patterns).
For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.}
%
These restrictions call for new avenues for solving the interpretation challenges of natural language models, which motivates the proposed work.

@@

    \item The NLIZE system that implements the perturbation exploration scheme by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback;
    %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
    %\item Perform error analysis by examining the stability of the predictions under perturbation;

    \item An optimization scheme for correcting a failed prediction based on a natural extension of the margin-infused relaxed algorithm (MIRA) to neural networks; and
    % to minimally update the model to fix a failed prediction, which help reason about the  better understand the re the question about how t

    \item A visual encoding of the attention by imposing sentence linguistic structure to allow grammar-guided sentence simplification.
\end{itemize}
%
% In addition,

>>>>

Compared to image classification tasks, natural language processing (NLP) systems often involve additional challenges such as the discrete nature of words.
For example, \emph{feature visualization}~\cite{OlahMordvintsevSchubert2017}, an often deployed technique for illustrating what image features a given part of the network (e.g., neuron, layer, or channel) captures, cannot be readily generalized to natural language.
\shusen{
An image (pixel values) corresponds to a continuous solution space. which is more accessible for optimization and human visual recognition (i.e., the existence or the absence of patterns).
For natural language, even though we can encode a word as a vector~\cite{MikolovSutskeverChen2013, PenningtonSocherManning2014}, the word embedding space is still discretely defined, in which the interpolation of two vectors (i.e., two words) does not hold clear meaning.}
%
These restrictions call for new avenues for solving the interpretation challenges of natural language models, which motivates the proposed work.

@@

    \item The NLIZE system that enables the perturbation-driven exploration by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback;
    %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
    %\item Perform error analysis by examining the stability of the predictions under perturbation;

    \item An optimization method for correcting a failed prediction based on a natural extension of the margin-infused relaxed algorithm (MIRA) to neural networks; and
    % to minimally update the model to fix a failed prediction, which help reason about the  better understand the re the question about how t

    \item A visual encoding of the attention by imposing sentence linguistic structure to allow grammar-guided sentence simplification.

\end{itemize}
%
% In addition,
